Spec2Fab: A High-Fidelity Mapping from Specification to Fabrication

### 2012-10-08 paper.tex
add caustic image
add figure for composing generators

\section{Built-in Components}
We provide a built-in library that handles common tasks such as assigning texture,
simulating deformation, and optimizing for a stacking.
\subsection{Generator}
\begin{enumerate}
\item A generator that uses a uniform grids with homogeneous
material in each grid cell. (A foam structure is treated as one homogeneous material).
\item A generator that decomposes a mesh into columns of stackings where each
column can be addressed separately by Generator::chooseSection.
This is useful for problems where local changes don't global effects such as
matching texture, matching mechanical properties of each column.
\item A polynomial spline representation for modifying the surface mesh.
\item A polynomial spline for height field of internal material layers (does not modify
surface mesh).
\end{enumerate}

@@

\subsection{Subsurface Scattering, Deformation and Mass}
Combining previous work on replicating
subsurface scattering and deformation behavior, 
we produced
material with a particular
look and deformation properties as shown in Figure~\ref{fig:deform}.
We als considered one additional property:mass. In this example, we
tried to make the material as light as possible.
\section{Caustics for a Mesh}
We demonstrate how to produce a 3D model with specific caustic shape under a particular lighting,
similar to \cite{Finckh:2010}. The difference is that we optimize on an arbitrary 3D model,
and we use a generic rendering package (NVidia optiX). Our algorithm took 6 hours to finish
with $4000$ spline control points for the model and $600\times 600$ resolution for the caustic image. A 
picture of our printed result under desired lighting is shown in Figure~\ref{fig:caustic}.

\begin{figure}
\begin{subfigure}[b]{0.3\textwidth}
	\centering
 	\includegraphics[width=\textwidth]{figure/slab_origin.png}
   	\caption{}
    \label{fig:deformPhoto}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.3\textwidth}
    \centering
  	\includegraphics[width=\textwidth]{figure/slab_deform.png}
    \caption{}
    \label{fig:deformPrint}
\end{subfigure}
\caption{Simutaneously matching appearance and deformation. 
(a)Original slab of a particular looking. (b)printed slab 
with the same looking and desired deformation.}
\label{fig:deform}
\end{figure}

@@

>>>>

\section{Built-in Components}
We provide a built-in library that handles common tasks such as assigning texture,
simulating deformation, and optimizing for a stacking.
\subsection{Generator}
Generator uses a reduced representation
of material assignments.
Each generator is defined over a domain in the input shape.
We provide a few basic generators and a composition operator.
Let the input shape be over a domain $\Omega$.
The composition of two generators $G_2\circ G_1$ is implemented by
first letting $G_1$ reduce over a domain $\Omega_1$ and
then letting $G_2$ reduce $\Omega_2 = \Omega-\Omega_1$.
An example is shown in Figure~\ref{fig:genCompose}
\begin{figure}[h]
\includegraphics[scale=0.2]{figure/genCompose.png}
\caption{Composition of two generators. $G_1$ is a fine-grained
surface voxelization and $G_2$ is a very coarse inner
grid.}
\label{fig:genCompose}
\end{figure}
\begin{enumerate}
\item A generator that uses a uniform grids with homogeneous
material in each grid cell. (A foam structure is treated as one homogeneous material).
\item A generator that decomposes a mesh into columns of stackings where each
column can be addressed separately by Generator::chooseSection.
This is useful for problems where local changes don't global effects such as
matching texture, matching mechanical properties of each column.
\item A polynomial spline representation for modifying the surface mesh.
\item A polynomial spline for height field of internal material layers (does not modify
surface mesh).
\end{enumerate}

@@

\subsection{Subsurface Scattering, Deformation and Mass}
Combining previous work on replicating
subsurface scattering and deformation behavior, 
we produced
material with a particular
look and deformation properties as shown in Figure~\ref{fig:deform}.
We als considered one additional property:mass. In this example, we
tried to make the material as light as possible.
\begin{figure}
\begin{subfigure}[b]{0.3\textwidth}
	\centering
 	\includegraphics[width=\textwidth]{figure/slab_origin.png}
   	\caption{}
    \label{fig:deformPhoto}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.3\textwidth}
    \centering
  	\includegraphics[width=\textwidth]{figure/slab_deform.png}
    \caption{}
    \label{fig:deformPrint}
\end{subfigure}
\caption{Simutaneously matching appearance and deformation. 
(a)Original slab of a particular looking. (b)printed slab 
with the same looking and desired deformation.}
\label{fig:deform}
\end{figure}

@@

\section{Caustics for a Mesh}
We demonstrate how to produce a 3D model with specific caustic shape under a particular lighting,
similar to \cite{Finckh:2010}. The difference is that we optimize on an arbitrary 3D model,
and we use a generic rendering package (NVidia optiX). Our algorithm took 6 hours to finish
with $4000$ spline control points for the model and $600\times 600$ resolution for the caustic image. A 
picture of our printed result under desired lighting is shown in Figure~\ref{fig:caustic}.

\begin{figure}
	\centering
 	\includegraphics[width=0.3\textwidth]{figure/caustic.jpg}
\caption{Teapot with a caustic image.}
\label{fig:caustic}
\end{figure}
